---
title: "googledrive tutorial"
author: "Jake Eisaguirre"
date: "7/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```

```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages

librarian::shelf(googledrive, here, tidyverse)

```

### Authenticate `Rstudio` and `googledrive`
```{r}
#drive_auth(email = "insert google drive connected email")
```


### The basics of the `googledrive` package


#### `drive_find` will search by file properties or text patterns. 
```{r}

drive_find(n_max = 30)

drive_find(type = "csv")

drive_find(pattern = "frog")

drive_find(pattern = ".rds")
```


#### `drive_get` will find and show all files and ID's in a specific folder. You can point to a folder locations with a direct URL. A dribble is created with 3 variables, the name of the folder, unique id for the folder, and a drive resource.
```{r}
modeling_folder <- drive_get("https://drive.google.com/drive/folders/1uWqLha9Gz1dkUXMkf6JWmMcBxDpso6Wp")

modeling_folder_id <- modeling_folder$id
```

#### Or you can point to folder locations with folder or file IDs
```{r}
drive_get(id = "1uWqLha9Gz1dkUXMkf6JWmMcBxDpso6Wp")

drive_get(id = modeling_folder_id)
```

#### the `as_id` function is another method for determinning id of a folder or file
```{r}
drive_get(as_id("https://drive.google.com/drive/folders/1uWqLha9Gz1dkUXMkf6JWmMcBxDpso6Wp"))

```

#### `drive_ls` function is the same as `ls` in the command line. It lists all the files with in that directory, google drive url, or google drive id
```{r}
drive_ls(modeling_folder)

```

#### `drive_rm` function is same as `rm` in the command line. Will remove the folder or file from the google drive
```{r}
drive_rm("insert folder/file name or id")
```


### Example how to download a set of model outputs within a folder
```{r}

model_output_folder <- "https://drive.google.com/drive/folders/1uWqLha9Gz1dkUXMkf6JWmMcBxDpso6Wp"

model_output_folder_id <- drive_get(as_id(model_output_folder))

files <- drive_ls(model_output_folder_id) 

for (i in files$id){
  drive_download(file = as_id(i), path = paste0(here("data"), "/", i), overwrite = T)
}

# inlcude `path = ` to point specific location where to download files


```

### Example how to download single file and to data folder and rename
```{r}

# file = name or id of specified file of interest
# path = local path to download too
# type = file type for saving

drive_download(file = "merged_AmphibianCaptureSurvey", path = here("data", "penn_amphib.csv"), type = "csv", overwrite = T)

```

### `drive_upload` will upload files or folders to the pointed google drive folder
```{r}
# media = local path
# path = path to google drive. Use the 'as_id' for ease

data_management_folder <- "https://drive.google.com/drive/folders/1ILolJkIp-NVEupfa877TgpUgRjkAqJdp"

data_management_folder_id <- drive_get(as_id(data_management_folder))

drive_upload(media = here("data", "penn_amphib.csv"), path = as_id(data_management_folder_id))

```




